### 2022-06-07 main/chapter_2ljets.tex
add zjets alt table

>>>>

Table~\ref{tab:2ljets_zjets_alt}

\begin{table}[tp]
\centering
\begin{tabular}{lcc}
& Central
& Relative variations
\\[0.5em]
CR-DY
& $59.64$
& $1-0.1+0.1$
\\[0.2em]
\underline{CR-Z}
& $101.95$
& $1+0.2-0.2$
\\[0.2em]
CR-tt
& $38.07$
& $1+0.5-0.5$
\\[0.2em]
CR-VZ
& $5.03$
& $1+1.3-1.0$
\\[0.5em]
VR-Low
& $24.19$
& $1-0.3+0.3$
\\[0.2em]
VR-Low-2
& $17.05$
& $1+0.2-0.2$
\\[0.5em]
\underline{SR-Low-a}
& $14.30$
& $1-0.2+0.2$
\\[0.2em]
\underline{SR-Low-b}
& $4.17$
& $1-0.3+0.3$
\\[0.2em]
SR-Low-2
& $1.51$
& $1+1.5-1.0$
\\[0.2em]
\end{tabular}
\caption[%
Alternative $\zjets$ variations in selected regions
]{%
Alternative $\zjets$ variations in selected regions.
The `Central' column shows the central $\zjets$ yield from the main sample.
The other column shows the relative scale factors applied to this central yield
for up and down variations.
These are evaluated from the central and alternative samples as described in
the text.
Note how up and down variations can move in different directions.
}
\label{tab:2ljets_zjets_alt}
\end{table}
